### 2019-04-07 papers/journal/model.tex
Moved the discussion about the size of the system upfront
Section 3 is completed

\noindent In this section, we will present our formal model of VTS.
%
Our model attempts to capture only the relevant aspects of the
system to develop understanding the flow structure of VTSs.
%
The model assumes that a cell consists of clearly defined compartments
that are well stirred within themselves.
%
The model assumes that all chemical reactions get sufficient time to complete.
%
The model describes stable flow of molecules and does not
capture the transient nature of VTSs.
%
The model also does not capture concentrations of the molecules and
only captures their presence or absence.
%

In the model, the compartments are nodes of a graph
and vesicles are the edges between the nodes.
%
There is a set of relevant molecules that participate in
management of the VTS.
%
Both nodes and edges are labelled with subsets of the molecules.
%
The molecules are activity and their control is defined using
activity functions and a pairing matrix.
%

@@

% \textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of type $Q$ and one of type $R$ or vice versa.
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.
% $\pairs(M'')$ are not active in any other node.

% We will also consider several variations of the model.
% %
% For example, the unique edge between two nodes, the activity of molecules is
% not constrained by $\nodef$ and $\edgef$, etc.
%

\vspace{0.2cm}
%\subsection{Uniform}
\noindent
A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
%
For a molecule $m \in M$,
an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
each $ 0 < i < \ell$.
%
A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
$n,...,n'$ in $G$.
%
% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
% $m$-path $n,...,n'$ in $G$.
%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
$n$ is $m$-reachable from $n'$.
%
The definition of stability implies that if a molecule leaves a
compartment then there must be a path for it to come back.
%
It ensures that the flow of molecules does not deplete a
compartment.
%
Such a property is often expected in several physical systems
such that electromagnetic fields, fluid dynamics, etc.

>>>>

\noindent In this section, we will present our formal model of VTS.
%
Our model attempts to capture only the relevant aspects of the
system to develop an understanding of the flow structure of VTSs.
%
The model assumes that a cell consists of clearly defined compartments
that are well stirred within themselves.
%
The model assumes that all chemical reactions get sufficient time to complete.
%
The model describes the stable flow of molecules and does not
capture the transient nature of VTSs.
%
The model also does not capture concentrations of the molecules and
only captures their presence or absence.
%

In the model, the compartments are nodes of a graph
and vesicles are the edges between the nodes.
%
There is a set of relevant molecules that participate in the management of the VTS.
%
Both nodes and edges are labeled with subsets of the molecules.
%
The molecules activity and their control is defined using
activity functions and a pairing matrix.
%

@@

% \textbf{Fusion condition in QBF and synthesis:}
%
A molecule $k$ is {\em active} at node $n$ if $k \in \nlabel(n)$ and
$\nodef(k,\nlabel(n))$ is true.
%
A molecule $k$ is {\em active} at edges $(n,M',n')$ if $k \in M'$ and
$\edgef(k,M')$ is true.
%
We say $G$ is {\em fuse compatible} if molecules $M$ is divided into
two partitions $Q$ and $R$ such that
for each $P \in \pairs, |P \intersect Q| = 3 \land |P \intersect R| = 1 $.
%
In other words,
molecules are of two types $Q$ and $R$,
%
pairing relations have sets of four molecules such that three
are of type $Q$ and one of type $R$ or vice versa.
%
% This distinction of molecules is due to section~\ref{mol-types}.
%
We call $G$ {\em well-structured} if it is pair compatible, and
for each $(n,M',n') \in \edges$, $n \neq n'$ and
$M' \subseteq \nlabel(n) \intersection \nlabel(n')$.
%
In addition to fuse compatibility, the well-structured property requires that
here are no self-loops, and 
each edge carry only those molecules that are present in its source
and destination nodes.
%
An edge $(n,M',\_) \in \edges$ {\em fuses} with a node $n'$
if there are non-empty set of molecules $M'' \subseteq M'$ and $M''' \subseteq \nlabel(n')$
such that $M''$ are active in the edge, $M'''$ are active in $n'$, and $M'' \union M''' \in \pairs$.
%
We call $G$ {\em well-fused} if each edge $(n,M',n') \in \edges$ fuses
with its destination node $n'$
and can not fuse with any other node.
%
$\pairs$ models biological possible quadruple of molecules that participate in fusion.
%
Each edge must be uniquely supported by such a quadruple of molecules.
%
We also require three of them to be on the node or edge, and the forth one
to be on the other side of the fusion.
% $\pairs(M'')$ are not active in any other node.

% We will also consider several variations of the model.
% %
% For example, the unique edge between two nodes, the activity of molecules is
% not constrained by $\nodef$ and $\edgef$, etc.
%
%
\vspace{0.2cm}
%\subsection{Uniform}
\noindent
A {\em path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,\_,n_{i+1}) \in \edges$ for each $ 0 < i < \ell$.
%
For a molecule $m \in M$,
an {\em $m$-path} in $G$ is a sequence $n_1,...,n_\ell$ of nodes 
such that $(n_i,M',n_{i+1}) \in \edges$ and $m \in M'$ for
each $ 0 < i < \ell$.
%
A node $n'$ is {\em ($m$-)reachable} from node $n$ in $G$ if there is a ($m$-)path
$n,...,n'$ in $G$.
%
% A node $n'$ is {\em $m$-reachable} from node $n$ in $G$ if there is a
% $m$-path $n,...,n'$ in $G$.
%
We call $G$ {\em stable} if for each $(n,M',n') \in \edges$ and $m \in M'$,
$n$ is $m$-reachable from $n'$.
%
The definition of stability implies that if a molecule leaves a
compartment then there must be a path for it to come back.
%
It ensures that the flow of molecules does not deplete a
compartment.
%
Such a property is often expected in several physical systems
such that electromagnetic fields, fluid dynamics, etc.
